\textbf{OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units}

### 2017-02-09 submission/Westcott_OptiClust_mSphere_2016.tex
Render write.paper on axiom

\includegraphics[width=6.0in]{results/figures/performance.png}

@@

\includegraphics[width=3.5in]{results/figures/speed_memory.png}

@@

\includegraphics[width=3.5in]{results/figures/split_mcc.png}

@@

\includegraphics[width=6.0in]{results/figures/performance_other.png}

@@

\includegraphics[width=3.5in]{results/figures/optimization.png}

>>>>

@@

@@

@@

\textbf{Table S1. Summary of the average number of true positives, true
negatives, false positives, false negatives and the resulting Matthews
correlation coefficient for each of the clustering methods that were
analyzed in this study for each of the six datasets.} Blank values
indicate that those conditions could not be completed in 50 hours with
45 GB of RAM.

@@
